gtsummary

### 2020-12-18 rmarkdown-gtsummary.Rmd
updates

```{r}
tbl1 <-
  glm(response ~ age + grade, trial, family = binomial) %>%
  tbl_regression(exponentiate = TRUE) %>%
  add_global_p()

tbl2 <-
  coxph(Surv(ttdeath, death) ~ age + grade, trial) %>%
  tbl_regression(exponentiate = TRUE) %>%
  add_global_p()

>>>>

```{r}
tbl1 <-
  glm(response ~ age + grade, trial, family = binomial) %>%
  tbl_regression(exponentiate = TRUE)

tbl2 <-
  coxph(Surv(ttdeath, death) ~ age + grade, trial) %>%
  tbl_regression(exponentiate = TRUE)
